QPLIB: A Library of Quadratic Programming Instances

### 2018-02-04 QPLIB-1.0.tex
suggestions

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. It is, therefore, perhaps not surprising that, unlike for ``simpler'' problems classes \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP. While several specialized libraries devoted to particular cases of QP are available, each of them is either focused on a particular application (a specific problem that can be modeled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.

>>>>

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. It is, therefore, perhaps not surprising that, unlike for ``simpler'' problems classes like Mixed-Integer Linear Programming \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP.\todo{AG: many commas in this sentence} While several specialized libraries devoted to particular cases of QP are available, each of them is either focused on a particular application (a specific problem that can be modeled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.

### 2018-02-04 QPLIB.tex
more accurate description of the advantages of .qplib provided
remove todonotes include
packages
fixup references and add a question as todo
fix typos
suggestions

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{calc}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{doi}
\usepackage[english]{babel}
\usepackage{microtype}

% TODO remove these before submission
\usepackage{todonotes}
%\usepackage{showlabels}

@@

%\newcommand{\half}{{\scriptstyle \frac{1}{2}}}
%\newcommand{\sfrac}[2]{{\scriptstyle \frac{#1}{#2}}}
\newcommand{\half}{\frac{1}{2}}

@@

%\listoftodos
\newpage

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP), i.e., the family of continuous and (mixed)-integer optimization problems where the objective function, the constrains, or both are quadratic.
 QP is a very ``varied'' class of problems, comprising sub-classes of problems ranging from
 trivial to undecidable. Solution methods for QP are very diverse, ranging from
 entirely combinatorial ones to completely continuous ones, including many for
 which both aspects are fundamental. Selecting a set of instances of QP that is
 at the same time not overwhelmingly onerous but sufficiently challenging for the
 many different interested communities is therefore important. We propose a simple
 taxonomy for QP instances that leads to a systematic problem selection mechanism.
 We then briefly survey the field of QP, giving an overview of theory, methods and
 solvers. Finally, we describe how the library was put together, and detail its final
 contents.
\end{abstract}

@@

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Acknowledgements}

We are grateful to all the donors who provided instances for the library. We gratefully acknowledge the financial support of the Gaspard Monge Program for Optimization and operations research (PGMO)  and the logistic support of GAMS for having provided us with the license of their software. Finally, we would like to acknowledge the financial and networking support by the COST Action TD1207.
The work of the fifth and twelfth author was supported by the Research Campus MODAL \emph{Mathematical Optimization and Data Analysis Laboratories} funded by the Federal Ministry of Education and Research (BMBF Grant~05M14ZAM).  All responsibilty for the content of this publication is assumed by the authors.

>>>>

\usepackage{url}
\usepackage{secdot}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{calc}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{doi}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage[normalem]{ulem}
\usepackage{todonotes}

@@

%\newcommand{\half}{{\scriptstyle \frac{1}{2}}}
%\newcommand{\sfrac}[2]{{\scriptstyle \frac{#1}{#2}}}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\Leo}[1]{{\color{red}#1}}

@@

\newpage

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP), i.e., the family of continuous and (mixed)-integer optimization problems where the objective function, the constrains, or both are quadratic.
 QP is a very diverse class of problems, comprising sub-classes of problems ranging from
 trivial to undecidable. This diversity is reflected in the variety of solution methods for QP, ranging from
 entirely combinatorial ones to completely continuous ones, including many for
 which both aspects are fundamental. Selecting a set of instances of QP that is
 at the same time not overwhelmingly onerous but sufficiently challenging for the
 many different interested communities is therefore important. We propose a simple
 taxonomy for QP instances that leads to a systematic problem selection mechanism.
 We then briefly survey the field of QP, giving an overview of theory, methods and
 solvers. Finally, we describe how the library was put together, and detail its final
 contents.
\end{abstract}

@@

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Acknowledgments}

We are grateful to all the donors who provided instances for the library. We gratefully acknowledge the financial support of the Gaspard Monge Program for Optimization and operations research (PGMO)  and the logistic support of GAMS for having provided us with the license of their software. Finally, we would like to acknowledge the financial and networking support by the COST Action TD1207.
The work of the fifth and twelfth author was supported by the Research Campus MODAL \emph{Mathematical Optimization and Data Analysis Laboratories} funded by the Federal Ministry of Education and Research (BMBF Grant~05M14ZAM).
The work of the sixth author was supported by the EPSRC grant EP/M025179/1.
All responsibility for the content of this publication is assumed by the authors.
